Creating the ``r params$package_name`` R package

### 2025-10-07 create-FSHybridPLS.Rmd
pasted normalize.all

```{r package-setup, message=FALSE, results='hide'}
usethis::create_package(
  path = ".",
  fields = list(
    Package = params$package_name,
    Version = "0.0.0.9000",
    Title = "A Package That Says Hello",
    Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
    Imports = "fda (>= 6.1.3), Matrix",
    `Authors@R` = person(
      given = "First",
      family = "Last",
      email = "you@gmail.com",
      role = c("aut", "cre")
      )
  )
)
usethis::use_mit_license(copyright_holder = "F. Last")
```

@@

```
## Documenting the package and building

>>>>

```{r package-setup, message=FALSE, results='hide'}
usethis::create_package(
  path = ".",
  fields = list(
    Package = params$package_name,
    Version = "0.0.0.9000",
    Title = "A Package That Says Hello",
    Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
    Imports = "fda (>= 6.1.3), Matrix, funData, foreach, irlba, refund",
    `Authors@R` = person(
      given = "First",
      family = "Last",
      email = "you@gmail.com",
      role = c("aut", "cre")
      )
  )
)
usethis::use_mit_license(copyright_holder = "F. Last")
```

@@

# Simulation tools

## sample splitting

```{r}
create_idx_train_test <-function(n_sample, train_ratio){
  n_train <- floor(n_sample*train_ratio)
  idx_train <- sort(sample(n_sample,n_train, replace=F))
  idx_test <- sort((1 : n_sample)[-idx_train])
  return(list(
    idx_train = idx_train, idx_test = idx_test
  ))
}
```

```{r}
create_idx_kfold <- function(n_sample, n_fold){
  idx_list <- caret::createFolds( (1 : n_sample), k = n_fold, list = TRUE, returnTrain = FALSE)
  idx_list_list <- list()
  for (i in 1:length(idx_list)){
    valid_hyper_index <- idx_list[[i]]
    train_hyper_index <- (1 : n_sample)[-valid_hyper_index]
    idx_list_list[[i]] <- list("idx_train" = train_hyper_index, "idx_valid" = valid_hyper_index)
  }
  return(idx_list_list)
}
```

```{r}
n_sample.fd <- function(fd_obj){
  length(fd_obj$fdnames$reps)
}
```

```{r}
normailize.all <- function(split.all_obj){
  curve_normalize_result_1 <- curve_normalize_train_test_fd(
    split.all_obj$data_fun_1_train,
    split.all_obj$data_fun_1_test)
  data_fun_1_train <- curve_normalize_result_1$train
  data_fun_1_test <- curve_normalize_result_1$test

  curve_normalize_result_2 <- curve_normalize_train_test_fd(
    split.all_obj$data_fun_2_train,
    split.all_obj$data_fun_2_test)
  data_fun_2_train <- curve_normalize_result_2$train
  data_fun_2_test <- curve_normalize_result_2$test

  scalar_normalize_result <- scalar_normalize_train_test(
    split.all_obj$data_scalar_train,
    split.all_obj$data_scalar_test)
  data_scalar_train <- scalar_normalize_result$train
  data_scalar_test <- scalar_normalize_result$test

  between_normalize_result <- btwn_normalize_train_test(
    list(data_fun_1_train, data_fun_2_train),
    data_scalar_train,
    data_scalar_test
  )
  data_scalar_train <- between_normalize_result$train
  data_scalar_test <- between_normalize_result$test

  response_mean_train <-  mean(split.all_obj$response_train)
  response_train <- split.all_obj$response_train - response_mean_train
  response_test <- split.all_obj$response_test - response_mean_train

  return(
    list(
      data_fun_1_train = data_fun_1_train,
      data_fun_2_train = data_fun_2_train,
      data_scalar_train= data_scalar_train,
      response_train   = response_train,
      data_fun_1_test  = data_fun_1_test,
      data_fun_2_test  = data_fun_2_test,
      data_scalar_test = data_scalar_test,
      response_test    = response_test
    )
  )
}
```

# Baseline method: FPCA regression

functions in MFPCA packages use an internal function calcBasisIntegrals. Somehow, this function did not work well on our simulations setting. Thus we modify the codes 
```{r}

# define global variable j, used by the foreach package and confusing R CMD CHECK
globalVariables('j')

#' Utility function that calculates matrix of basis-scalar products (one dimension)
#'
#' If the element \eqn{X^{(j)}}{X^{(j)}} is expanded in basis functions \eqn{b_i^{(j)}(t),~ i = 1, \ldots, K_j}{b_i(t)},
#' this function calculates the \eqn{K_j \times K_j}{K_j  \times K_j} matrix \eqn{B^{(jj)}}{B^{(jj)}} with entries
#' \deqn{B^{(jj)}_{mn} = \int_{\mathcal{T_j}} b_m^{(j)}(t) b_n^{(j)}(t) \mathrm{d} t}.
#'
#' @section Warning: This function is implemented only for functions on one- or two-dimensional domains.
#'
#' @param basisFunctions Array of \code{npc} basis functions of dimensions \code{npc x M1} or \code{npc x M1 x M2}.
#' @param dimSupp dimension of the support of the basis functions (1 or 2)
#' @param argvals List of corresponding x-values.
#'
#' @return A matrix containing the scalar product of all combinations of basis functions (matrix \eqn{B^{(j)}})
#'
#' @seealso \code{\link{MFPCA}}, \code{\link[funData]{dimSupp}}
#'
#' @keywords internal
calcBasisIntegrals <- function(basisFunctions, dimSupp, argvals)
{
  npc <- dim(basisFunctions)[1]

  #  integral basis matrix
  B <- array(0, dim = c(npc, npc))

  if(dimSupp == 1) # one-dimensional domain
  {
    w <- funData::.intWeights(argvals[[1]])

    for(m in seq_len(npc))
    {
      for(n in seq_len(m))
        B[m, n] <- B[n, m] <- (basisFunctions[m, ]* basisFunctions[n, ])%*%w
    }
  }
  else # two-dimesional domain (otherwise function stops before!)
  {
    w1 <- t(funData::.intWeights(argvals[[1]]))
    w2 <- funData::.intWeights(argvals[[2]])

    for(m in seq_len(npc))
    {
      for(n in seq_len(m))
        B[m, n] <- B[n, m] <-  w1 %*%(basisFunctions[m, , ]* basisFunctions[n, ,])%*%w2
    }
  }

  return(B)
}
```

###   Multivariate functional principal component analysis for functions on different (dimensional) domains

- This function calculates a multivariate functional principal component analysis (MFPCA) based on i.i.d. observations $x_1, \ldots, x_N$ of a multivariate functional data-generating process $X = (X^{(1)}, \ldots  X^{(p)})}{X = X^(1), \ldots, X^(p)$ with elements $X^{(j)} \in L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)$ defined on a domain $\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}$.
- In particular, the elements can be defined on different (dimensional) domains.
- The results contain the mean function, the estimated multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure as $x_i$), the associated eigenvalues $\hat \nu_1 \geq \ldots \geq \hat \nu_M > 0$ and the individual scores \eqn{\hat \rho_{im} = \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}.

- Univariate Expansions
    - The multivariate functional principal component analysis relies on a univariate basis expansion for each element $X^{(j)}$.
    - The univariate basis representation is calculated using the univDecomp function, that passes the univariate functional observations and optional parameters to the specific function.
    - The univariate decompositions are specified via the uniExpansions argument in the MFPCA function.
    - It is a list of the same length as the mFData object, i.e. having one entry for each element of the multivariate functional data.
    - For each element, uniExpansion must specify at least the type of basis functions to use.
    - Additionally, one may add further parameters.
    - The following basis representations are supported: \itemize{
        -  Given basis functions. Then \code{uniExpansions[[j]] = list(type = "given", functions)}, where \code{functions} is a \code{funData} object on the same domain as \code{mFData}, containing the given basis functions. 
        - Univariate functional principal component analysis. Then \code{uniExpansions[[j]] = list(type = "uFPCA", nbasis, pve, npc, makePD)}, where \code{nbasis,pve,npc,makePD} are parameters passed to the \code{\link{PACE}} function for calculating the univariate functional principal component analysis.
        - Basis functions expansions from the
  package \pkg{fda}. Then \code{uniExpansions[[j]] = list(type = "fda", ...)},
#' where \code{...} are passed to \code{\link[funData]{funData2fd}}, which
#' heavily builds on \code{\link[fda]{eval.fd}}. If \pkg{fda} is not available,
#' a warning is thrown.
\item Spline basis functions (not penalized). Then
#' \code{uniExpansions[[j]] = list(type = "splines1D", bs, m, k)}, where
#' \code{bs,m,k} are passed to the functions \code{\link{univDecomp}} and
#' \code{\link{univExpansion}}. For two-dimensional tensor product splines, use
#' \code{type = "splines2D"}. 
\item Spline basis functions (with smoothness
#' penalty). Then \code{uniExpansions[[j]] = list(type = "splines1Dpen", bs, m,
#' k)}, where \code{bs,m,k} are passed to the functions \code{\link{univDecomp}}
#' and \code{\link{univExpansion}}. Analogously to the unpenalized case, use
#' \code{type = "splines2Dpen"} for 2D penalized tensor product splines. 
\item
#' Cosine basis functions. Use \code{uniExpansions[[j]] = list(type = "DCT2D",
#' qThresh, parallel)} for functions one two-dimensional domains (images) and
#' \code{type = "DCT3D"} for 3D images. The calculation is based on the discrete
#' cosine transform (DCT) implemented in the C-library \code{fftw3}. If this
#' library is not available, the function will throw  a warning. \code{qThresh}
#' gives the quantile for hard thresholding the basis coefficients based on
#' their absolute value. If \code{parallel = TRUE}, the coefficients for
#' different images are calculated in parallel.} See \code{\link{univDecomp}}
#' and \code{\link{univExpansion}} for details.}

```{r}
#'
#' @export MFPCA
MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
                  bootstrap = FALSE, nBootstrap = NULL, bootstrapAlpha = 0.05, bootstrapStrat = NULL,
                  verbose = options()$verbose)
{
  if(! inherits(mFData, "multiFunData"))
    stop("Parameter 'mFData' must be passed as a multiFunData object.")

  # number of components
  p <- length(mFData)
  # number of observations
  N <- nObs(mFData)

  if(!all(is.numeric(M), length(M) == 1, M > 0))
    stop("Parameter 'M' must be passed as a number > 0.")

  if(!(is.list(uniExpansions) & length(uniExpansions) == p))
    stop("Parameter 'uniExpansions' must be passed as a list with the same length as 'mFData'.")

  if(!(is.numeric(weights) & length(weights) == p))
    stop("Parameter 'weights' must be passed as a vector with the same length as 'mFData'.")

  if(!is.logical(fit))
    stop("Parameter 'fit' must be passed as a logical.")

  if(!is.logical(approx.eigen))
    stop("Parameter 'approx.eigen' must be passed as a logical.")

  if(!is.logical(bootstrap))
    stop("Parameter 'bootstrap' must be passed as a logical.")

  if(bootstrap)
  {
    if(is.null(nBootstrap))
      stop("Specify number of bootstrap iterations.")

    if(any(!(0 < bootstrapAlpha & bootstrapAlpha < 1)))
      stop("Significance level for bootstrap confidence bands must be in (0,1).")

    if(!is.null(bootstrapStrat))
    {
      if(!is.factor(bootstrapStrat))
        stop("bootstrapStrat must be either NULL or a factor.")

      if(length(bootstrapStrat) != nObs(mFData))
        stop("bootstrapStrat must have the same length as the number of observations in the mFData object.")
    }
  }

  if(!is.logical(verbose))
    stop("Parameter 'verbose' must be passed as a logical.")

  # dimension for each component
  dimSupp <- dimSupp(mFData)

  # get type of univariate expansions
  type <- vapply(uniExpansions, function(l){l$type}, FUN.VALUE = "")

  # de-mean functions -> coefficients are also de-meaned!
  # do not de-mean in uFPCA, as PACE gives a smooth estimate of the mean (see below)
  m <- meanFunction(mFData, na.rm = TRUE) # ignore NAs in data
  for(j in seq_len(p))
  {
    if(type[j] != "uFPCA")
      mFData[[j]] <- mFData[[j]] - m[[j]]
  }

  if(verbose)
    cat("Calculating univariate basis expansions (", format(Sys.time(), "%T"), ")\n", sep = "")

########### modified by Jongmin Mun #############################
  # calculate univariate basis expansion for all components
  uniBasis <- mapply(
    function(expansion, data, data_predict){
      do.call(univDecomp, c(
        list(funDataObject = data, funDataObject_predict = data_predict),
        expansion)
        )
      },
    expansion = uniExpansions,
    data = mFData,
    data_predict = mFData_predict,
    SIMPLIFY = FALSE
    )
########### modified by Jongmin Mun #############################

  # for uFPCA: replace estimated mean in m
  for(j in seq_len(p))
  {
    if(type[j] == "uFPCA")
      m[[j]] <- uniBasis[[j]]$meanFunction
  }

  # Multivariate FPCA
  npc <- vapply(uniBasis, function(x){dim(x$scores)[2]}, FUN.VALUE = 0) # get number of univariate basis functions

  if(M > sum(npc))
  {
    M <- sum(npc)
    warning("Function MFPCA: total number of univariate basis functions is smaller than given M. M was set to ", sum(npc), ".")
  }

  # check if non-orthonormal basis functions used
  if(all(foreach::foreach(j = seq_len(p), .combine = "c")%do%{uniBasis[[j]]$ortho}))
    Bchol = NULL
  else
  {
    # Cholesky decomposition of B = block diagonal of Cholesky decompositions
    Bchol <- Matrix::bdiag(lapply(uniBasis, function(l){
      if(l$ortho)
        res <- Matrix::Diagonal(n = ncol(l$scores))
      else
        res <- Matrix::chol(l$B)

      return(res)}))
  }

  if(verbose)
    cat("Calculating MFPCA (", format(Sys.time(), "%T"), ")\n", sep = "")

  mArgvals <- if (utils::packageVersion("funData") <= "1.2") {
    getArgvals(mFData)
  } else {
    funData::argvals(mFData)
  }

  res <- calcMFPCA(N = N, p = p, Bchol = Bchol, M = M, type = type, weights = weights,
                   npc = npc, argvals = mArgvals, uniBasis = uniBasis, fit = fit, approx.eigen = approx.eigen)

  res$meanFunction <- m # return mean function, too

  names(res$functions) <- names(mFData)

  #############modified by jongmin mun

  #####################################
  if(fit)
  {
    res$fit <- m + res$fit # add mean function to fits
    names(res$fit) <- names(mFData)
  }

  # give correct names
  namesList <- lapply(mFData, names)
  if(!all(vapply(namesList, FUN = is.null, FUN.VALUE = TRUE)))
  {
    if(length(unique(namesList)) != 1)
      warning("Elements have different curve names. Use names of the first element for the results.")

    row.names(res$scores) <- namesList[[1]]

    if(fit)
      for(i in seq_len(p))
        names(res$fit[[i]]) <- namesList[[1]]
  }

  if(type[1] == "uFPCA"){
    scores.pred<-calcMFPCA_predict(N = nObs(mFData_predict),
                      p = p,
                      M = M,
                      weights = weights,
                      npc = npc,
                      uniBasis = uniBasis,
                      normFactors = res$normFactors,
                      vectors_train=res$vectors,
                      values_train=res$values
    )
  }
  res$scores.pred <- scores.pred

  class(res) <- "MFPCAfit"
    return(res)
}

### calcMFPCA
```{r}
#' Internal function that implements the MFPCA algorithm for given univariate decompositions
#' @export
calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
{
  # combine all scores
  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}

  # block vector of weights
  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}

  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)

  # check if approximation is appropriate (cf. irlba)
  if(approx.eigen & (M > min(N, sum(npc))/2))
  {
    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
            'approx.eigen' set to FALSE.")
    approx.eigen = FALSE
  }

  # check if non-orthonormal basis functions used and calculate PCA on scores
  if(is.null(Bchol))
  {
    if(approx.eigen)
    {
      tmpSVD <- irlba::irlba(as.matrix(Z), nv = M)

      vectors <- tmpSVD$v
      values <- tmpSVD$d[seq_len(M)]^2
    }
    else
    {
      if(sum(npc) > 1000)
        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")

      e <- eigen(stats::cov(allScores) * outer(allWeights, allWeights, "*"))

      values <- e$values[seq_len(M)]
      vectors <- e$vectors[,seq_len(M)]
    }
  }
  else
  {
    if(approx.eigen)
    {
      tmpSVD <- irlba::irlba(as.matrix(Matrix::tcrossprod(Z, Bchol)), nv = M)

      vectors <- Matrix::crossprod(Bchol, tmpSVD$v)
      values <- tmpSVD$d[seq_len(M)]^2
    }
    else
    {
      if(sum(npc) > 1000)
        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")

      e <- eigen(Matrix::crossprod(Bchol) %*% (stats::cov(allScores) * outer(allWeights, allWeights, "*")))

      values <- Re(e$values[seq_len(M)])
      vectors <- Re(e$vectors[,seq_len(M)])
    }
  }

  # normalization factors
  normFactors <- 1/sqrt(diag(as.matrix(Matrix::crossprod(Z %*% vectors))))

  ### Calculate scores
  scores <- Z %*% vectors * sqrt(N-1) # see defintion of Z above!
  scores <- as.matrix(scores %*% diag(sqrt(values) * normFactors, nrow = M, ncol = M)) # normalization

  ### Calculate eigenfunctions (incl. normalization)
  npcCum <- cumsum(c(0, npc)) # indices for blocks (-1)

  tmpWeights <- as.matrix(Matrix::crossprod(Z, Z %*%vectors))
  eFunctions <- foreach::foreach(j = seq_len(p)) %do% {
    univExpansion(type = type[j],
                  scores = 1/sqrt(weights[j] * values) * normFactors * t(tmpWeights[npcCum[j]+seq_len(npc[j]), , drop = FALSE]),
                  argvals = argvals[[j]],
                  functions = uniBasis[[j]]$functions,
                  params = uniBasis[[j]]$settings)
  }

  res <- list(values = values,
              functions = multiFunData(eFunctions),
              scores = scores,
              vectors = vectors,
              values = values,
              normFactors = normFactors,
              uniBasis = uniBasis,
              uniExpansions = uniExpansions
  )

  # calculate truncated Karhunen-Loeve representation (no mean here)
  if(fit)
    res$fit <- multivExpansion(multiFuns = res$functions, scores = scores)

  return(res)
}
```

### calcMFPCA

```{r}
#' Internal function that implements the MFPCA algorithm for given univariate decompositions
#' @export
#' 
calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
{
  # combine all scores
  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}

  # block vector of weights
  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}

  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)

  # check if approximation is appropriate (cf. irlba)
  if(approx.eigen & (M > min(N, sum(npc))/2))
  {
    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
            'approx.eigen' set to FALSE.")
    approx.eigen = FALSE
  }

  # check if non-orthonormal basis functions used and calculate PCA on scores
  if(is.null(Bchol))
  {
    if(approx.eigen)
    {
      tmpSVD <- irlba::irlba(as.matrix(Z), nv = M)

      vectors <- tmpSVD$v
      values <- tmpSVD$d[seq_len(M)]^2
    }
    else
    {
      if(sum(npc) > 1000)
        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")

      e <- eigen(stats::cov(allScores) * outer(allWeights, allWeights, "*"))

      values <- e$values[seq_len(M)]
      vectors <- e$vectors[,seq_len(M)]
    }
  }
  else
  {
    if(approx.eigen)
    {
      tmpSVD <- irlba::irlba(as.matrix(Matrix::tcrossprod(Z, Bchol)), nv = M)

      vectors <- Matrix::crossprod(Bchol, tmpSVD$v)
      values <- tmpSVD$d[seq_len(M)]^2
    }
    else
    {
      if(sum(npc) > 1000)
        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")

      e <- eigen(Matrix::crossprod(Bchol) %*% (stats::cov(allScores) * outer(allWeights, allWeights, "*")))

      values <- Re(e$values[seq_len(M)])
      vectors <- Re(e$vectors[,seq_len(M)])
    }
  }

  # normalization factors
  normFactors <- 1/sqrt(diag(as.matrix(Matrix::crossprod(Z %*% vectors))))

  ### Calculate scores
  scores <- Z %*% vectors * sqrt(N-1) # see defintion of Z above!
  scores <- as.matrix(scores %*% diag(sqrt(values) * normFactors, nrow = M, ncol = M)) # normalization

  ### Calculate eigenfunctions (incl. normalization)
  npcCum <- cumsum(c(0, npc)) # indices for blocks (-1)

  tmpWeights <- as.matrix(Matrix::crossprod(Z, Z %*%vectors))
  eFunctions <- foreach::foreach(j = seq_len(p)) %do% {
    univExpansion(type = type[j],
                  scores = 1/sqrt(weights[j] * values) * normFactors * t(tmpWeights[npcCum[j]+seq_len(npc[j]), , drop = FALSE]),
                  argvals = argvals[[j]],
                  functions = uniBasis[[j]]$functions,
                  params = uniBasis[[j]]$settings)
  }

  res <- list(values = values,
              functions = multiFunData(eFunctions),
              scores = scores,
              vectors = vectors,
              values = values,
              normFactors = normFactors,
              uniBasis = uniBasis,
              uniExpansions = uniExpansions
  )

  # calculate truncated Karhunen-Loeve representation (no mean here)
  if(fit)
    res$fit <- multivExpansion(multiFuns = res$functions, scores = scores)

  return(res)
}
```

### calcMFPCA_predict

```{r}
#' calcMFPCA_predict
#' @export
#' 
calcMFPCA_predict <- function(N, p, M, weights, npc, uniBasis,
                              normFactors_train, vectors_train, values_train)
{
  # combine all scores
  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores.pred}

  # block vector of weights
  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}

  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)

  ### Calculate scores
  scores <- Z %*% vectors_train * sqrt(N-1) # see defintion of Z above!
  scores <- as.matrix(scores %*% diag(sqrt(values_train) * normFactors_train, nrow = M, ncol = M)) # normalization

  return(scores)
}

```{r}
load("C:/Users/jongmin/Documents/GitHub/fsPLS/simul/graphical_high_correlation/graphical_data.RData")
```

```{r}
library(refund)
eval_point<-seq(1, 100, length.out = 100)
n_iter_max = 40
n_basis_predictor = 10
n_scalar <- 9
library(foreach)
library(funData)
uniExpansions <- list(
  list(type = "uFPCA", nbasis = n_basis_predictor, npc = n_iter_max),
  list(type = "uFPCA", nbasis = n_basis_predictor, npc = n_iter_max)
)

n_fold = 5
n_scalar <- 9
rmse_simul_fpca <- matrix(NA, nrow = n_rep, ncol = 3)
colnames(rmse_simul_fpca) <- c("FPC+PC", "FPC_only", "PC_only")
```

```{r}

  train_test_idx <- create_idx_train_test(n_sample, train.ratio)
  train_test_split <- split.all(data_fun_1[[rep_number]], data_fun_2[[rep_number]], data_scalar[[rep_number]], response[[rep_number]], train_test_idx)
  train_test_split_normalized <- normailize.all(train_test_split)

  kfold_idx <- create_idx_kfold(length(train_test_idx$idx_train), n_fold)
  cv_mat <- matrix(0, nrow = n_iter_max, ncol = n_scalar)
  for (fold_num in 1:n_fold){
    cat(paste0(fold_num, "th fold\n"))
    #train-valid split (5 fold)
    train_valid_idx <- kfold_idx[[fold_num]]
    cv_train_valid_split <- split.all(
      train_test_split$data_fun_1_train, train_test_split$data_fun_2_train, train_test_split$data_scalar_train, train_test_split$response_train,
      train_valid_idx)

    #normalizing
    cv_train_valid_split_normalized <- normailize.all(cv_train_valid_split)

    #format

    predictor_cv_train <- multiFunData(
      fd2funData(cv_train_valid_split_normalized$data_fun_1_train, eval_point),
      fd2funData(cv_train_valid_split_normalized$data_fun_2_train, eval_point)
    )
    predictor_cv_valid <- multiFunData(
      fd2funData(cv_train_valid_split_normalized$data_fun_1_test, eval_point),
      fd2funData(cv_train_valid_split_normalized$data_fun_2_test, eval_point)
    )

    # train FPCA

    MFPCA_fit_cv <- MFPCA(mFData = predictor_cv_train, mFData_predict = predictor_cv_valid, M = n_iter_max, uniExpansions = uniExpansions)

    #train scalar PCA
    PCA_fit_train <- prcomp(cv_train_valid_split_normalized$data_scalar_train, center=F, scale = F)
    #validate
    for (n_fpc in 1:n_iter_max){
      for (n_spc in 1:n_scalar){
        cat(paste(n_fpc, n_spc, "\n"))
        FPC_score_cv <- (MFPCA_fit_cv$scores)[ ,(1:n_fpc)]
        PC_score_cv <- (PCA_fit_train$x)[ , (1:n_spc)]
        pc_score_cv_combined <- data.frame(cv_train_valid_split_normalized$response_train, FPC_score_cv, PC_score_cv)
        colnames(pc_score_cv_combined) <- c(
          c("response"),
          paste0( rep("FPC", n_fpc), as.character(1:n_fpc)),
          paste0( rep("PC", n_spc), as.character(1:n_spc))
        )

        # fit linear regression
        rank_now <- rankMatrix(pc_score_cv_combined[,-1])[1]
        print(rank_now)
        cat(paste("rank deficient:", (n_fpc + n_spc)-rank_now, "\n"))
        linear_fit_cv <- lm(response~., data = pc_score_cv_combined)

        #validation set pc scores
        PFC_score_valid <- (MFPCA_fit_cv$scores.pred)[ ,(1:n_fpc)]
        PC_score_valid <- (predict(PCA_fit_train, cv_train_valid_split_normalized$data_scalar_test))[ , (1:n_spc)]
        pc_score_valid_combined <- data.frame(PFC_score_valid, PC_score_valid)
        colnames(pc_score_valid_combined) <- c(
          paste0( rep("FPC", n_fpc), as.character(1:n_fpc)),
          paste0( rep("PC", n_spc), as.character(1:n_spc))
          )

        y_pred <- predict(linear_fit_cv, pc_score_valid_combined)
        cv_mat[n_fpc, n_spc] <- cv_mat[n_fpc, n_spc] +
          sqrt( mean( sum( (y_pred - cv_train_valid_split_normalized$response_test)^2 ) ))
        }
    }
  }
    n_iter_best <- arrayInd(which.min(cv_mat), dim(cv_mat))
    n_fpc_best  <- n_iter_best[1]
    n_spc_best  <- n_iter_best[2]
    print(n_fpc_best)
    print(n_spc_best)

    predictor_final_train <- multiFunData(
      fd2funData(train_test_split_normalized$data_fun_1_train, eval_point),
      fd2funData(train_test_split_normalized$data_fun_2_train, eval_point)
    )
    predictor_final_test <- multiFunData(
      fd2funData(train_test_split_normalized$data_fun_1_test, eval_point),
      fd2funData(train_test_split_normalized$data_fun_2_test, eval_point)
    )

    # train FPCA and scalar PCA
    MFPCA_fit_final <- MFPCA(mFData = predictor_final_train, mFData_predict = predictor_final_test, M = n_fpc_best, uniExpansions = uniExpansions)
    PCA_fit_final <- prcomp(train_test_split_normalized$data_scalar_train, center=F, scale = F)
    PFC_score_final_train <- MFPCA_fit_final$scores
    PC_score_final_train <- (predict(PCA_fit_final, train_test_split_normalized$data_scalar_train))[,c(1:n_spc_best)]
    pc_score_final_train_combined <- data.frame(train_test_split_normalized$response_train, PFC_score_final_train, PC_score_final_train)
    colnames(pc_score_final_train_combined) <- c(
      c("response"),
      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best)),
      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
    )
    linear_fit_final <- lm(response~., data = pc_score_final_train_combined)

    # test set pc scores
    PFC_score_final_test <- MFPCA_fit_final$scores.pred
    PC_score_final_test <- (predict(PCA_fit_final, train_test_split_normalized$data_scalar_test))[,c(1:n_spc_best)]
    pc_score_final_test_combined <- data.frame(PFC_score_final_test, PC_score_final_test)
    colnames(pc_score_final_test_combined) <- c(
      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best)),
      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
    )
    y_pred_final <- predict(linear_fit_final, pc_score_final_test_combined)
    rmse_simul_fpca[rep_number,1] <- sqrt(
      mean((y_pred_final - train_test_split_normalized$response_test)^2)
      )
    print(rmse_simul_fpca[rep_number,1])

    plot(-0.2:0.2, -0.2:0.2, pch = "", xlim = c(-0.2, 0.2),  ylim = c(-0.2, 0.2))
    plot(train_test_split_normalized$response_test, y_pred_final)
    abline(a=0, b=1)

    pc_score_final_train_combined_fpc_only <- data.frame(train_test_split_normalized$response_train, PFC_score_final_train)
    colnames(pc_score_final_train_combined_fpc_only) <- c(
      c("response"),
      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best))
    )
    linear_fit_final_fpc_only <- lm(response~., data = pc_score_final_train_combined_fpc_only)
    pc_score_final_test_combined_fpc_only <- data.frame(PFC_score_final_test)
    colnames(pc_score_final_test_combined_fpc_only) <- c(
      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best))
    )
    y_pred_final_fpc_only <- predict(linear_fit_final_fpc_only, pc_score_final_test_combined_fpc_only)
    rmse_simul_fpca[rep_number,2] <- sqrt(
      mean((y_pred_final_fpc_only - train_test_split_normalized$response_test)^2)
    )
    print(rmse_simul_fpca[rep_number,2])

    pc_score_final_train_combined_spc_only <- data.frame(train_test_split_normalized$response_train, PC_score_final_train)
    colnames(pc_score_final_train_combined_spc_only) <- c(
      c("response"),
      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
    )
    linear_fit_final_spc_only <- lm(response~., data = pc_score_final_train_combined_spc_only)
    pc_score_final_test_combined_spc_only <- data.frame(PC_score_final_test)
    colnames(pc_score_final_test_combined_spc_only) <- c(
      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
    )
    y_pred_final_spc_only <- predict(linear_fit_final_spc_only, pc_score_final_test_combined_spc_only)
    rmse_simul_fpca[rep_number,3] <- sqrt(
      mean((y_pred_final_spc_only - train_test_split_normalized$response_test)^2)
    )
    print(rmse_simul_fpca[rep_number,3])

## Documenting the package and building
